---
title: "Assignment 3 - Regression Models"
authors: "Adrian David Sauter, Eloy Rafael González"
date: "21746 Data Mining 2022-23"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
dat <- read.csv("king.csv")
head(dat)
```
```{r}
all(dat$X==dat$ID)
```
Since the X- and ID-column contain the same information and are irrelevant 
in predicting the housing price, we can get rid of them.
```{r}
dat$X <- NULL
dat$ID <- NULL
```
## 1 - THE DATA
```{r}
summary(dat$price)
hist(log(dat$price), main = "Histogram of log(price)", xlab="#price")
```

The mean is greater than the median. This tells us that the distribution is slightly
right-skewed. 
```{r}
summary(dat)
```
### Number of bedrooms
```{r}
plot(log(dat$price)~dat$bedrooms, xlab="#bedrooms", ylab="log(price)")
```
As we can see, the relation between this two variables isn't linear.

```{r}
cor(dat$price,dat$bedrooms)
```
```{r}
max(dat$bedrooms)
```
There is one very strange outlier with 33 bedrooms. What does the correlation 
coefficient look like without that outlier?
```{r}
cor(dat[dat$bedrooms<30, "price"], dat[dat$bedrooms<30, "bedrooms"])
```
The correlation coefficient does go up a little bit, but not significantly.

Data distribution:
```{r}
summary(dat$bedrooms)
table(dat$bedrooms)
```
```{r}
hist(log(dat$bedrooms), main="Histogram of log(bedrooms)", xlab="#bedrooms")
```
The data is not that equally distributed, but rather right-skewed (mean > 
median). Especially strange is the outlier with 33 bedrooms (which was most likely a typo).

### Number of bathrooms
```{r}
plot(log(dat$price)~dat$bathrooms, xlab="#bathrooms", ylab="log(price)")
```
We can see that in this case there's some linear correlation, since the prices ,generally, slowly rise the more bathrooms the house has.

```{r}
cor(dat$price, dat$bathrooms)
```
Regarding the number of bedrooms and bathrooms, it can be seen that for both
instances, there is a positive correlation (meaning higher price for larger 
number of bath-/bedrooms and vice versa). However, as can be seen in the plot 
and the correlation coefficient, this holds better for bathrooms than for 
bedrooms. After peaking around 6 bedrooms, the price tends to decrease again with
increasing number of bedrooms. For bathrooms, the price has the tendency to 
increase with larger number of bathrooms.

Data distribution:
```{r}
summary(dat$bathrooms)
table(dat$bathrooms)
```
```{r}
hist(log(dat$bathrooms), main="Histogram of log(bathrooms)", xlab="#bathrooms")
```

The data is not normally distributed

### Number of square feet of the house
```{r}
plot(log(dat$price)~dat$sqft_living, xlab="#sqft of the home", 
     ylab="log(price)")
```

We can see that there's a relationship between this variables but it seems like the progression is more logarithmic than linear.

```{r}
cor(dat$price, dat$sqft_living)
```

Data distribution:
```{r}
summary(dat$sqft_living)
```
```{r}
hist(log(dat$sqft_living), main="Histogram of log(sqft_living)", xlab="sqft_living")
```
Although not with exact precision, the data seems normally distributed.

### Number of square feet of the lot
```{r}
plot(log(dat$price)~dat$sqft_lot, xlab="#sqft of the lot", ylab="log(price)")
```
There's no linear correlation between this variables.

```{r}
cor(dat$price, dat$sqft_lot)
```
The square footage of the home seems to be a far better predictor of the price
than the square footage of the lot. This can be seen both in the higher correlation coefficient of square footage of the home as well as in the plot. 

Data distribution:
```{r}
summary(dat$sqft_lot)
```
```{r}
hist(log(dat$sqft_lot), main="Histogram of log(sqft_lot)", xlab="sqft_lot")
```
This variable doesn't quite follow a normal distribution

### Number of floors
```{r}
boxplot(log(dat$price)~dat$floors, xlab="#floors", ylab="price")
```
```{r}
cor(dat$price, dat$floors)
```
The first thing that pops out here is that the "number of floors"-feature 
doesn't consist of only integers. It's not quite clear to me what a house 
with 2.5 floors looks like, but either way, there is somewhat of a small 
positive correlation between the number of floors and the housing price.

Data distribution:
```{r}
summary(dat$floors)
table(dat$floors)
```
```{r}
hist(dat$floors, main = "Histogram of floors", xlab="#floors")
```
This variable doesn't follow a normal distribution.

### View to waterfront
Transform feature to factor:
```{r}
dat$waterfront <- as.factor(dat$waterfront)
levels(dat$waterfront) <- c("No-Waterfront", "Waterfront")
```

```{r}
boxplot(log(dat$price)~dat$waterfront, xlab="view to waterfront", 
     ylab="log(price)")
```

```{r}
mean(dat[dat$waterfront=="No-Waterfront", "price"])
```
```{r}
mean(dat[dat$waterfront=="Waterfront", "price"])
```
It can already be seen in the plot, but the calculation of the mean price based
on whether the house has a view to a waterfront or not makes it even more 
obvious: houses with a view to a waterfront have higher prices than houses 
without that view. 

Data distribution:
```{r}
summary(dat$waterfront)
table(dat$waterfront)
```
There are many more houses without a waterfront view than houses with a waterfront view.
### Number of views
```{r}
boxplot(log(dat$price)~dat$view, xlab="#times the house has been viewed", 
        ylab="log(price)")
```
```{r}
cor(dat$price, dat$view)
```
Once again, we have a positive correlation that can also be seen in the plot: 
The more times a house has been viewed, the higher the price of the house tends
to be on average.
From the plot, it looks like the houses with 0 views have a lot more outliers
regarding the price than houses with more views. Let's take a look at this:
```{r}
summary(dat[dat$view==0, "price"])
```

```{r}
# get the number of outliers (below lower whisker of boxplot or above upper
# whisker). Whiskers are calculated by:
# (1st_quartile) - 1.5*(IQR) = (1st_quartile) - 1.5*(3rd_quartile-1st_quartile)
# and 
# (3rd_quartile) + 1.5*(IQR) = (3rd_quartile) + 1.5*(3rd_quartile-1st_quartile)
length(dat[dat$view==0 
           & log(dat$price) < log(312000) - 1.5*(log(600000)-log(312000))
           | log(dat$price) > log(600000) + 1.5*(log(600000)-log(312000)),
           "price"])
```
The fraction outliers/total_number_observations is more suitable to discover
the amount of outliers for a specific value of a feature:
```{r}
length(dat[dat$view==0 
           & log(dat$price) < log(312000) - 1.5*(log(600000)-log(312000))
           | log(dat$price) > log(600000) + 1.5*(log(600000)-log(312000)),
           "price"]) / length(dat[dat$view==0, "price"])
```
Let's do the same for the other values of dat$view:
```{r}
summary(dat[dat$view==1, "price"])
```
```{r}
length(dat[dat$view==1 
           & log(dat$price) < log(515750) - 1.5*(log(947500)-log(515750))
           | log(dat$price) > log(947500) + 1.5*(log(947500)-log(515750)),
           "price"]) / length(dat[dat$view==1, "price"])
```
```{r}
summary(dat[dat$view==2, "price"])
```
```{r}
length(dat[dat$view==2 
           & log(dat$price) < log(489500) - 1.5*(log(935500)-log(489500))
           | log(dat$price) > log(935500) + 1.5*(log(935500)-log(489500)),
           "price"]) / length(dat[dat$view==2, "price"])
```
```{r}
summary(dat[dat$view==3, "price"])
```
```{r}
length(dat[dat$view==3 
           & log(dat$price) < log(582525) - 1.5*(log(1320000)-log(582525))
           | log(dat$price) > log(1320000) + 1.5*(log(1320000)-log(582525)),
           "price"]) / length(dat[dat$view==2, "price"])
```
```{r}
summary(dat[dat$view==4, "price"])
```
```{r}
length(dat[dat$view==4 
           & log(dat$price) < log(811000) - 1.5*(log(1705000)-log(811000))
           | log(dat$price) > log(1705000) + 1.5*(log(1705000)-log(811000)),
           "price"]) / length(dat[dat$view==2, "price"])
```
The highest outlier-to-non-outlier-ratio can be found for view==1, although the
graph indicates that view==0 has the highest number of outliers. However, this
higher number of outliers is most likely due to the fact that many houses have 
view==0 and therefore, it's naturally more probable to observe more outliers 
than with fewer data samples. This is also supported by the fact that for 
view==0, the standard deviation is not maximal for all view==i [i=0,1,2,3,4]:
```{r}
aggregate(dat$price, list(dat$view), FUN=sd)
```

Data distribution
```{r}
summary(dat$view)
table(dat$view)
```
Most of the houses haven't been viewed yet.
### Condition of the house
Transform feature to factor:
```{r}
dat$condition <- as.factor(dat$condition)
levels(dat$condition) <- c("Bad Condition", "Average Condition", "Good Condition", "Very Good Condition", "Excellent Condition")
```
```{r}
boxplot(log(dat$price)~dat$condition, xlab="Condition of the house", 
        ylab="log(price)")
```
```{r}
aggregate(dat$price~dat$condition, FUN=mean)
```
It can be seen that the price tends to go up with a better condition of the 
house.

Data distribution:
```{r}
table(dat$condition)
```

There aren't many houses with a value of 1 or 2 regarding condition. 
Most of the houses are in a good or better than good condition.
### Grade of the house
```{r}
boxplot(log(dat$price)~dat$grade, xlab="grade of the house", ylab="log(price)")
```
```{r}
cor(dat$price, dat$grade)
```
There is a nice positive correlation between the price of the house and the 
grade given to the house. The higher the grade - the more expensive the house 
tends to be.

Data distribution:
```{r}
summary(dat$grade)
table(dat$grade)
hist(dat$grade, main="Histogram of grade", xlab="#grade")
```
The data is right-skewed, most of the houses have a rating of >= 6.

### Square feet of the house (apart from basement)
```{r}
plot(log(dat$price)~dat$sqft_above, xlab="sqft of the house", 
     ylab="log(price)")
```
We can see that there's a relationship between those variables although it seems more logarithmic than linear.
```{r}
cor(dat$price, dat$sqft_above)
```
Once again, the fairly large positive correlation coefficient supports what can
be already seen in the plot: The higher the number of sqft in the house, the 
higher the price tends to be. Let's split the category into ranges and take 
another look at the data:
```{r}
dat$sqft_above_1000_range <- cut(dat$sqft_above, breaks=seq(0,9000,1000), 
                             labels=c("1-1000", "1001-2000", "2001-3000", 
                                      "3001-4000", "4001-5000", "5001-6000",
                                      "6001-7000", "7001-8000", "8001-9000"))
head(dat[, c("sqft_above", "sqft_above_1000_range")])
```
```{r}
plot(log(dat$price)~dat$sqft_above_1000_range, 
     xlab="sqft of the house (without basement) in range of 1000",
     ylab="log(price)")
```
The trend "more sqft -> higher price" can be seen much easier in this plot.

Data distribution:
```{r}
table(dat$sqft_above_1000_range)
```
```{r}
summary(dat$sqft_above)
hist(dat$sqft_above)
```

Most houses are in the 1001-2000 range. The distribution is right-skewed

### Number of square feet of the basement
```{r}
plot(log(dat$price)~dat$sqft_basement, xlab="sqft of the basement", 
     ylab="log(price)")
```
It can be seen that in general the price grows linearly with this variable. Specially if we don't take into account the case where sqft_basement=0.
```{r}
cor(dat$price, dat$sqft_basement)
```
It can be seen in the plot that there are a lot of houses that don't have any 
basement (dat$sqft_basement==0). What is the fraction of houses without a 
basement?
```{r}
length(dat[dat$sqft_basement==0, "sqft_basement"]) / length(dat$sqft_basement)
```
```{r}
cor(dat[dat$sqft_basement!=0, "price"], 
    dat[dat$sqft_basement!=0, "sqft_basement"])
```
Not taking into account houses without a basement results in a higher 
correlation coefficient.
```{r}
summary(dat$sqft_basement)
```


```{r}
hist(dat$sqft_basement, main="Histogram of sqft_basement", xlab="sqft basement")
```
The distribution is right-skewed


### Year built
```{r}
plot(log(dat$price)~dat$yr_built, xlab="year built", ylab="log(price)")
```
It's hard to see the trends very well in this plot, so let's add another column 
in which the yr_built-variable is separated into ranges of 10 years.
```{r}
dat$yr_built_10_range <- cut(dat$yr_built, breaks=seq(1900,2020,10), 
                             labels=c("1900-1910", "1911-1920", "1921-1930", 
                                      "1931-1940", "1941-1950", "1951-1960", 
                                      "1961-1970", "1971-1980", "1981-1990", 
                                      "1991-2000", "2001-2010", "2011-2020"))
# check if it worked: 
head(dat[, c("yr_built", "yr_built_10_range")])
```

```{r}
boxplot(log(dat$price)~dat$yr_built_10_range, 
        xlab="yr_built in ranges of 10 years", ylab="log(price)")
```
Maybe ranges of 10 years make things more visible: 
```{r}
dat$yr_built_20_range <- cut(dat$yr_built, breaks=seq(1900,2020,20), 
                             labels=c("1900-1920", "1921-1940", "1941-1960", 
                                      "1961-1980", "1981-2000", "2001-2020"))
# check if it worked: 
head(dat[, c("yr_built", "yr_built_20_range")])
```
```{r}
boxplot(log(dat$price)~dat$yr_built_20_range, 
        xlab="yr_built in ranges of 20 years", ylab="log(price)")
```
```{r}
cor(dat$price,dat$yr_built)
```
There is no real trend to be seen in the plots. Along with the very low 
correlation coefficient, it seems as the yr_built-feature isn't a good 
indicator for the house price.

Data distribution:
```{r}
summary(dat$yr_built_10_range)
```
```{r}
hist(dat$yr_built, main="Histogram of yr_built", xlab="yr_built")
```
Yr_built doesn't follow a normal distribution.

### Year renovated
```{r}
plot(log(dat$price)~dat$yr_renovated, xlab="renovated year", ylab="log(price)")
```
Houses that weren't renovated have a value of dat$yr_renovated==0. This doesn't 
look good in the graph, so let's take a look at samples that have a value != 0.
```{r}
plot(log(dat[dat$yr_renovated!=0, "price"])~
       dat[dat$yr_renovated!=0, "yr_renovated"],
     xlab="renovation year", ylab="log(price)")
```
```{r}
cor(dat$price,dat$yr_renovated)
```
The yr_renovated-feature isn't a really good predictor. Is it better without 
the samples that weren't renovated?
```{r}
cor(dat[dat$yr_renovated!=0, "price"], dat[dat$yr_renovated!=0, "yr_renovated"])
```
There is no significant change.

Data distribution:
```{r}
hist(dat$yr_renovated, main="Histogram of yr_renovated", xlab="yr_renovated")
```
The data doesn't follow a normal distribution.

### Zipcode
```{r}
aggregate(dat$price, list(dat$zipcode), FUN=mean)
```
```{r}
boxplot(log(dat$price)~dat$zipcode, xlab="zipcode", ylab="log(price)")
```
It's difficult to learn something from the zipcode-feature because there are 
many different zipcodes and there is no information on how the zipcodes 
were distributed among the regions (i.e. if similar zipcodes also mean a 
geographical proximity).
However, if assumed that similar zipcodes mean geographical proximity,
it's possible to group the houses by zipcodes and then check if there is a 
more visible trend in the graph:
```{r}
dat$zipcode_20_range <- cut(dat$zipcode, breaks=seq(98000,98200,20), 
                             labels=c("98001-98020", "98021-98040", 
                                      "98041-98060", "98061-98080",
                                      "98081-98100", "98101-98120",
                                      "98121-98140", "98141-98160",
                                      "98161-98180", "98181-98200"))
# check if it worked: 
head(dat[, c("zipcode", "zipcode_20_range")])
```
```{r}
boxplot(log(dat$price)~dat$zipcode_20_range, 
        xlab="zipcodes, grouped in ranges of 20", ylab="log(price)")
```
No real trend can be seen when grouping the zipcodes. 

Data distribution:
```{r}
hist(dat$zipcode, main="Histogram of zipcode", xlab="zipcode")
```
The data doesn't follow a normal distribution.

### Latitude coordinate
```{r}
plot(log(dat$price)~dat$lat, xlab="latitude coordinate", ylab="log(price)")
```
Let's group the coordinates in order to get a better look at possible trends:

```{r}
dat$lat_005_range <- cut(dat$lat, breaks=seq(47.15, 47.80, 0.05), 
                         labels=c("47.11-47.20", "47.21-47.25", "47.26-47.30",
                                  "47.31-47.35", "47.36-47.40", "47.41-47.45",
                                  "47.46-47.50", "47.51-47.55", "47.56-47.60",
                                  "47.61-47.65", "47.66-47.70", "47.71-47.75",
                                  "47.76-47.80"))
head(dat[, c("lat", "lat_005_range")])
```
```{r}
plot(log(dat$price)~dat$lat_005_range, 
     xlab="latitude coordinate in ranges of 0.05", ylab="log(price)")
```
In this plot, it can be seen that the price is maximum for houses with a 
latitude coordinate in the range of 47.61-47.65. Lower and higher latitudes
result in a lower price generally.
```{r}
cor(dat$price, dat$lat)
```
There is a weak-medium positive correlation between the latitude coordinate and
the price of the house.

Data distribution:
```{r}
summary(dat$lat)
```
```{r}
hist(dat$lat, main="Histogram of lat", xlab="lat")
```
The distribution is left-skewed.

### Longitude coordinate
```{r}
plot(log(dat$price)~dat$long, xlab="longitude coordinate", ylab="log(price)")
```
Let's group the coordinates once again:

```{r}
# different notation used in order to make the ranges clear
dat$long_01_range <- cut(dat$long, breaks=seq(-122.6, -121.2, 0.1), 
                         labels=c("-122.6<x<=-122.5", "-122.5<x<=-122.4",
                                  "-122.4<x<=-122.3", "-122.3<x<=-122.2",
                                  "-122.2<x<=-122.1", "-122.1<x<=-122.0",
                                  "-122.0<x<=-121.9", "-121.9<x<=-121.8",
                                  "-121.8<x<=-121.7", "-121.7<x<=-121.6",
                                  "-121.6<x<=-121.5", "-121.5<x<=-121.4",
                                  "-121.4<x<=-121.3", "-121.3<x<=-121.2"))
head(dat[, c("long", "long_01_range")])
```

```{r}
boxplot(log(dat$price)~dat$long_01_range, 
        xlab="longitude coordinate in ranges of 0.1", ylab="log(price)")
```

```{r}
cor(dat$price, dat$long)
```
There is almost no correlation between the longitude coordinate and the price.

Data distribution:
```{r}
summary(dat$long)
hist(dat$long, main="Histogram of long", xlab="long")
```
The distribution is right-skewed.

### Square footage of interior housing of 15 closest neighbors
```{r}
dat$sqft_living15_500_range <- cut(dat$sqft_living15, breaks=seq(0, 6500, 500),
                                   labels=c("1-500", "501-1000", "1001-1500",
                                            "1501-2000", "2001-2500",
                                            "2501-3000", "3001-3500", 
                                            "3501-4000", "4001-4500",
                                            "4501-5000", "5001-5500",
                                            "5501-6000", "6001-6500"))
head(dat[, c("sqft_living15", "sqft_living15_500_range")])
```
```{r}
boxplot(log(dat$price)~dat$sqft_living15_500_range, 
        xlab="square foot of interior housing of 15 closest neighbors in 
        range of 500", ylab="log(price)")
```

```{r}
cor(dat$price, dat$sqft_living15)
```
The positive correlation coefficient supports what can be already seen in the 
graph: a higher number of dat$sqft_living15 goes hand in hand with a higher 
price in general. However, there's one box that goes against that trend in the 
plot above, i.e. the one in the 1-500 range. But that is due to the fact that 
there are only 2 samples in this range and this sould therefore not be regarded
as representative.

Data distribution:
```{r}
summary(dat$sqft_living15)
hist(dat$sqft_living15)
```
The distribution is right-skewed.

### Square footage of land lots of 15 closest neighbors
```{r}
plot(log(dat$price)~dat$sqft_lot15, 
     xlab="sqft of land lots of 15 closest neighbors", ylab="log(price)")
```
The graph is heavily influenced by the two outliers with a very value of 
sqft_lot15. Let's take a look at the distribution without these extreme 
outliers:
```{r}
tail(sort(dat$sqft_lot15))
```

Let's put the sqft_lot15-feature in ranges. Since most samples seem to 
be below 20000 sqft_lot15, I put all samples with values over 20000 in 
one category and the rest in smaller categories.
```{r}
dat$sqft_lot15_2000_range <- cut(dat$sqft_lot15, 
                                  breaks=c(seq(0, 20000, 2000), +Inf),
                                  labels=c("1-2000", "2001-4000",
                                           "4001-6000", "6001-8000",
                                           "8001-10000", "10001-12000",
                                           "12001-14000", "14001-16000",
                                           "16001-18000", "18001-20000",
                                           ">20000"))

head(dat[, c("sqft_lot15", "sqft_lot15_2000_range")])
```

```{r}
plot(log(dat$"price")~dat$sqft_lot15_2000_range,
     xlab="sqft of land lots of 15 closest neighbors in 2000 range",
     ylab="log(price)")
```
```{r}
cor(dat$price,dat$sqft_lot15)
```
There is almost no correlation between the sqft_lot15-feature and the price
of the houses. 

Now, it's time to select the most useful features. Let's take a look at the
correlations: 
```{r}
vct_corr <- numeric(0)
for (i in names(dat)){
    cor.result <- cor(dat$price, as.numeric(dat[, i]))
    vct_corr <- c(vct_corr, cor.result)
}
names(vct_corr) <- names(dat)
vct_corr
```
Let's remove all features with a low correlation:
```{r}
library(dplyr)
dat_red <- select(dat, c(price, bathrooms, sqft_living, grade, 
                     sqft_above, sqft_living15))
head(dat_red)
```
Now, let's eliminate outliers:
```{r}
orig_length = length(dat$price)
```

```{r}
b_sqft_living <- boxplot(dat_red$sqft_living)
```
Let's remove the samples for which the sqft_living-value is below the lower
or beyond the upper whisker:
```{r}
l1 <- length(dat_red$price)
dat_red <- dat_red[dat_red$sqft_living >= b_sqft_living$stats[1] &
                       dat_red$sqft_living <= b_sqft_living$stats[5], ]
l2 <- length(dat_red$price)
sprintf("old no. of samples: %s, new no. of samples: %s, new dataset contains %s%% of the samples of the old dataset", l1, l2, (100*l2)/l1)
```
Let's repeat that for the other features as well:
```{r}
b_grade <- boxplot(dat_red$grade)
l1 <- length(dat_red$price)
dat_red <- dat_red[dat_red$grade >= b_grade$stats[1] &
                       dat_red$grade <= b_grade$stats[5], ]
l2 <- length(dat_red$price)
sprintf("old no. of samples: %s, new no. of samples: %s, new dataset contains %s%% of the samples of the old dataset", l1, l2, (100*l2)/l1)
```
```{r}
b_sqft_above <- boxplot(dat_red$sqft_above)
l1 <- length(dat_red$price)
dat_red <- dat_red[dat_red$sqft_above >= b_sqft_above$stats[1] &
                       dat_red$sqft_above <= b_sqft_above$stats[5], ]
l2 <- length(dat_red$price)
sprintf("old no. of samples: %s, new no. of samples: %s, new dataset contains %s%% of the samples of the old dataset", l1, l2, (100*l2)/l1)
```
```{r}
b_sqft_living15 <- boxplot(dat_red$sqft_living15)
l1 <- length(dat_red$price)
dat_red <- dat_red[dat_red$sqft_living15 >= b_sqft_living15$stats[1] &
                       dat_red$sqft_living15 <= b_sqft_living15$stats[5], ]
l2 <- length(dat_red$price)
sprintf("old no. of samples: %s, new no. of samples: %s, new dataset contains %s%% of the samples of the old dataset", l1, l2, (100*l2)/l1)
```
```{r}
b_bathrooms <- boxplot(dat_red$bathrooms)
l1 <- length(dat_red$price)
dat_red <- dat_red[dat_red$bathrooms >= b_bathrooms$stats[1] &
                       dat_red$bathrooms <= b_bathrooms$stats[5], ]
l2 <- length(dat_red$price)
sprintf("old no. of samples: %s, new no. of samples: %s, new dataset contains %s%% of the samples of the old dataset", l1, l2, (100*l2)/l1)
```
```{r}
sprintf("Overall, the dataset contains now - after removing outliers - %s%% of the samples of the original dataset", (100*l2)/orig_length)
```
```{r}
summary(dat$sqft_lot15)
hist(log(dat$sqft_lot15), main="Histogram of log(sqft_lot15", xlab="sqft_lot15")
```
This distribution is right skewed
