---
title: "Assignment 3 - Regression Models"
authors: "Adrian David Sauter, Eloy Rafael González"
date: "21746 Data Mining 2022-23"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
dat <- read.csv("king.csv")
head(dat)
```
```{r}
all(dat$X==dat$ID)
```
Since the X- and ID-column contain the same information and are irrelevant 
in predicting the housing price, we can get rid of them.
```{r}
dat$X <- NULL
dat$ID <- NULL
```
## 1 - THE DATA
```{r}
summary(dat$price)
hist(dat$price, main = "Histogram of price", xlab="price")
```

The mean is greater than the median. This tells us that the distribution is 
slightly right-skewed. Let's log-transform the price-variable and check take 
another look at the distribution.
```{r}
dat$price <- log(dat$price)
hist(dat$price, main = "Histogram of log(price)", xlab="price")
```

The mean is greater than the median. This tells us that the distribution is slightly
right-skewed. 
```{r}
summary(dat)
```
### Number of bedrooms
```{r}
plot(dat$price~dat$bedrooms, xlab="#bedrooms", ylab="log(price)")
```

Since the number of bedrooms isn't a continuous variable, the distribution
can't look perfectly linear. However, it looks fairly linear. 

```{r}
cor(dat$price,dat$bedrooms)
```
```{r}
max(dat$bedrooms)
```
There is one very strange outlier with 33 bedrooms. What does the correlation 
coefficient look like without that outlier?
```{r}
cor(dat[dat$bedrooms<30, "price"], dat[dat$bedrooms<30, "bedrooms"])
```
The correlation coefficient does go up a little bit, but not significantly.

Data distribution:
```{r}
summary(dat$bedrooms)
table(dat$bedrooms)
```
```{r}
hist(dat$bedrooms, main="Histogram of bedrooms", xlab="#bedrooms")
```

The data is not that equally distributed, but rather right-skewed (mean > 
median). Especially strange is the outlier with 33 bedrooms 
(which was most likely a typo).

```{r}
plot(lm(price~bedrooms, data=dat), which=c(1,2))
```
The residual vs fitted plot shows a fairly linear trend with exception of the 
one outlier.
The normal Q-Q plot doesn't show any obvious departures from normality; the 
majority of the points are all fit the line.
### Number of bathrooms
```{r}
plot(dat$price~dat$bathrooms, xlab="#bathrooms", ylab="log(price)")
```

We can see that in this case there's some linear correlation, since the prices,
generally, slowly rise the more bathrooms the house has.

```{r}
cor(dat$price, dat$bathrooms)
```
Regarding the number of bedrooms and bathrooms, it can be seen that for both
instances, there is a positive correlation (meaning higher price for larger 
number of bath-/bedrooms and vice versa). However, as can be seen in the plot 
and the correlation coefficient, this holds better for bathrooms than for 
bedrooms. After peaking around 6 bedrooms, the price tends to decrease again 
with increasing number of bedrooms. For bathrooms, the price has the tendency to 
increase with larger number of bathrooms.

Data distribution:
```{r}
summary(dat$bathrooms)
table(dat$bathrooms)
```
```{r}
hist(dat$bathrooms, main="Histogram of bathrooms", xlab="#bathrooms")
```

The data is not normally distributed. 
```{r}
plot(lm(price~bathrooms, data=dat), which=c(1,2))
```
The residual vs fitted plot shows a fairly linear trend.
The normal Q-Q plot doesn't show any obvious departures from normality; the 
majority of the points are all fit the line.
### Number of square feet of the house
```{r}
plot(dat$price~dat$sqft_living, xlab="#sqft of the home", 
     ylab="log(price)")
```

We can see that there's a relationship between this variables but it seems like 
the progression is not quite linear but maybe quadratic or exponential.
```{r}
cor(dat$price, dat$sqft_living)
```
Data distribution:
```{r}
summary(dat$sqft_living)
```
```{r}
hist(dat$sqft_living, main="Histogram of sqft_living", 
     xlab="sqft_living")
```
The data doesn't look normally distributed, let's log-transform it:
```{r}
dat$sqft_living <- log(dat$sqft_living)
hist(dat$sqft_living, main="Histogram of log(sqft_living)", 
     xlab="log(sqft_living)")
```
Although not with exact precision, the data seems normally distributed.
```{r}
plot(lm(price~sqft_living, data=dat), which=c(1,2))
```

The residual vs fitted plot shows a quadratic linear trend.
The normal Q-Q plot doesn't show any obvious departures from normality; the 
majority of the points are all fit the line.
### Number of square feet of the lot
```{r}
plot(dat$price~dat$sqft_lot, xlab="#sqft of the lot", ylab="log(price)")
```
There's no linear correlation between these variables.

```{r}
cor(dat$price, dat$sqft_lot)
```
The square footage of the home seems to be a far better predictor of the price
than the square footage of the lot. This can be seen both in the higher 
correlation coefficient of square footage of the home as well as in the plot. 

Data distribution:
```{r}
summary(dat$sqft_lot)
```
```{r}
hist(dat$sqft_lot, main="Histogram of sqft_lot", xlab="sqft_lot")
```
Let's log-transform it: 
```{r}
dat$sqft_lot <- log(dat$sqft_lot)
hist(dat$sqft_lot, main="Histogram of log(sqft_lot)", xlab="log(sqft_lot)")
```

This variable doesn't quite follow a normal distribution.
```{r}
plot(lm(price~sqft_lot, data=dat), which=c(1,2))
```
The residual vs fitted plot shows a fairly linear trend.
The normal Q-Q plot doesn't show any obvious departures from normality; the 
majority of the points are all fit the line.
### Number of floors
```{r}
boxplot(dat$price~dat$floors, xlab="#floors", ylab="log(price)")
```
```{r}
cor(dat$price, dat$floors)
```
The first thing that pops out here is that the "number of floors"-feature 
doesn't consist of only integers. It's not quite clear to me what a house 
with 2.5 floors looks like, but either way, there is somewhat of a small 
positive correlation between the number of floors and the housing price.

Data distribution:
```{r}
summary(dat$floors)
table(dat$floors)
```
```{r}
hist(dat$floors, main = "Histogram of floors", xlab="#floors")
```
This variable doesn't follow a normal distribution.
```{r}
plot(lm(price~floors, data=dat), which=c(1,2))
```

The residual vs fitted plot shows a barely linear trend.
The normal Q-Q plot doesn't show any obvious departures from normality; the 
majority of the points are all fit the line.
### View to waterfront
Transform feature to factor:
```{r}
dat$waterfront <- as.factor(dat$waterfront)
levels(dat$waterfront) <- c("No-Waterfront", "Waterfront")
```

```{r}
boxplot(dat$price~dat$waterfront, xlab="view to waterfront", 
     ylab="log(price)")
```

```{r}
mean(dat[dat$waterfront=="No-Waterfront", "price"])
```
```{r}
mean(dat[dat$waterfront=="Waterfront", "price"])
```
It can already be seen in the plot, but the calculation of the mean price based
on whether the house has a view to a waterfront or not makes it even more 
obvious: houses with a view to a waterfront have higher prices than houses 
without that view. 
Data distribution:
```{r}
summary(dat$waterfront)
```
There are way more houses without a waterfront view than houses with a 
waterfront view.
### Number of views
```{r}
boxplot(dat$price~dat$view, xlab="#times the house has been viewed", 
        ylab="log(price)")
```
```{r}
cor(dat$price, dat$view)
```
Once again, we have a positive correlation that can also be seen in the plot: 
The more times a house has been viewed, the higher the price of the house tends
to be on average.
From the plot, it looks like the houses with 0 views have a lot more outliers
regarding the price than houses with more views. Let's take a look at this:
```{r}
summary(dat[dat$view==0, "price"])
```

```{r}
# get the number of outliers (below lower whisker of boxplot or above upper
# whisker). Whiskers are calculated by:
# (1st_quartile) - 1.5*(IQR) = (1st_quartile) - 1.5*(3rd_quartile-1st_quartile)
# and 
# (3rd_quartile) + 1.5*(IQR) = (3rd_quartile) + 1.5*(3rd_quartile-1st_quartile)
length(dat[dat$view==0 
           & dat$price < 12.65 - 1.5*(13.30-12.65)
           | dat$price > 13.30 + 1.5*(13.30-12.65),
           "price"])
```
The fraction outliers/total_number_observations is more suitable to discover
the amount of outliers for a specific value of a feature:
```{r}
length(dat[dat$view==0 
           & dat$price < 12.65 - 1.5*(13.30-12.65)
           | dat$price > 12.65 + 1.5*(13.30-12.65),
           "price"]) / length(dat[dat$view==0, "price"])
```
Let's do the same for the other values of dat$view:
```{r}
summary(dat[dat$view==1, "price"])
```
```{r}
length(dat[dat$view==1 
           & dat$price < 13.15 - 1.5*(13.76-13.15)
           | dat$price > 13.76 + 1.5*(13.76-13.15),
           "price"]) / length(dat[dat$view==1, "price"])
```
```{r}
summary(dat[dat$view==2, "price"])
```
```{r}
length(dat[dat$view==2 
           & dat$price < 13.10 - 1.5*(13.75-13.10)
           | dat$price > 13.75 + 1.5*(13.75-13.10),
           "price"]) / length(dat[dat$view==2, "price"])
```
```{r}
summary(dat[dat$view==3, "price"])
```
```{r}
length(dat[dat$view==3 
           & dat$price < 13.28 - 1.5*(14.09-13.28)
           | dat$price > 14.09 + 1.5*(14.09-13.28),
           "price"]) / length(dat[dat$view==2, "price"])
```
```{r}
summary(dat[dat$view==4, "price"])
```
```{r}
length(dat[dat$view==4 
           & dat$price < 13.61 - 1.5*(14.35-13.61)
           | dat$price > 14.35 + 1.5*(14.35-13.61),
           "price"]) / length(dat[dat$view==2, "price"])
```
The highest outlier-to-non-outlier-ratio can be found for view==1, although the
graph indicates that view==0 has the highest number of outliers. However, this
higher number of outliers is most likely due to the fact that many houses have 
view==0 and therefore, it's naturally more probable to observe more outliers 
than with fewer data samples. This is also supported by the fact that for 
view==0, the standard deviation is not maximal for all view==i [i=0,1,2,3,4]:
```{r}
aggregate(dat$price, list(dat$view), FUN=sd)
```
Data distribution
```{r}
summary(dat$view)
table(dat$view)
```
Most of the houses haven't been viewed yet.
```{r}
plot(lm(price~view, data=dat), which=c(1,2))
```

The residual vs fitted plot shows a fairly linear trend.
The normal Q-Q plot doesn't show any obvious departures from normality; the 
majority of the points are all fit the line.
### Condition of the house
Transform feature to factor:
```{r}
dat$condition <- as.factor(dat$condition)
levels(dat$condition) <- c("Bad Condition", "Average Condition", "Good Condition", "Very Good Condition", "Excellent Condition")
```
```{r}
boxplot(dat$price~dat$condition, xlab="Condition of the house", 
        ylab="log(price)")
```
```{r}
aggregate(dat$price~dat$condition, FUN=mean)
```
It can be seen that the price tends to go up with a better condition of the 
house.
Data distribution:
```{r}
table(dat$condition)
```
There aren't many houses with a value of 1 or 2 regarding condition. 
Most of the houses are in a good or better than good condition.
```{r}
plot(lm(price~condition, data=dat), which=c(1,2))
```

The residual vs fitted plot shows a fairly linear trend.
The normal Q-Q plot doesn't show any obvious departures from normality; the 
majority of the points are all fit the line.
### Grade of the house
```{r}
boxplot(dat$price~dat$grade, xlab="grade of the house", ylab="log(price)")
```
```{r}
cor(dat$price, dat$grade)
```
There is a nice positive correlation between the price of the house and the 
grade given to the house. The higher the grade - the more expensive the house 
tends to be.

Data distribution:
```{r}
summary(dat$grade)
table(dat$grade)
hist(dat$grade, main="Histogram of grade", xlab="grade")
```

The data is right-skewed, most of the houses have a rating of >= 6.
```{r}
plot(lm(price~grade, data=dat), which=c(1,2))
```

The residual vs fitted plot shows a fairly linear trend.
The normal Q-Q plot doesn't show any obvious departures from normality; the 
majority of the points are all fit the line.
### Square feet of the house (apart from basement)
```{r}
plot(dat$price~dat$sqft_above, xlab="sqft of the house", 
     ylab="log(price)")
```
We can see that there's a relationship between those variables although it 
doesn't seem quite linear.

```{r}
cor(dat$price, dat$sqft_above)
```
Once again, the fairly large positive correlation coefficient supports what can
be already seen in the plot: The higher the number of sqft in the house, the 
higher the price tends to be. Let's split the category into ranges and take 
another look at the data:
```{r}
dat$sqft_above_1000_range <- cut(dat$sqft_above, breaks=seq(0,9000,1000), 
                             labels=c("1-1000", "1001-2000", "2001-3000", 
                                      "3001-4000", "4001-5000", "5001-6000",
                                      "6001-7000", "7001-8000", "8001-9000"))
head(dat[, c("sqft_above", "sqft_above_1000_range")])
```
```{r}
plot(dat$price~dat$sqft_above_1000_range, 
     xlab="sqft of the house (without basement) in range of 1000",
     ylab="log(price)")
```
The trend "more sqft -> higher price" can be seen much easier in this plot.
Data distribution:
```{r}
table(dat$sqft_above_1000_range)
```
```{r}
summary(dat$sqft_above)
hist(dat$sqft_above)
```

The distribution is right-skewed. Let's log-transform the sqft_above-variable.
```{r}
dat$sqft_above <- log(dat$sqft_above)
hist(dat$sqft_above, main="Histogram of log(sqft_above)", 
     xlab="log(sqft_above)")
```

```{r}
plot(lm(price~sqft_above, data=dat), which=c(1,2))
```

The residual vs fitted plot shows a fairly quadratic trend.
The normal Q-Q plot doesn't show any obvious departures from normality; the 
majority of the points are all fit the line.
### Number of square feet of the basement
```{r}
plot(dat$price~dat$sqft_basement, xlab="sqft of the basement", 
     ylab="log(price)")
```
It can be seen that in general the price grows linearly with this variable. 
Specially if we don't take into account the case where sqft_basement=0.
```{r}
cor(dat$price, dat$sqft_basement)
```
It can be seen in the plot that there are a lot of houses that don't have any 
basement (dat$sqft_basement==0). What is the fraction of houses without a 
basement?
```{r}
length(dat[dat$sqft_basement==0, "sqft_basement"]) / length(dat$sqft_basement)
```
```{r}
cor(dat[dat$sqft_basement!=0, "price"], 
    dat[dat$sqft_basement!=0, "sqft_basement"])
```
Not taking into account houses without a basement results in a higher 
correlation coefficient.
```{r}
summary(dat$sqft_basement)
```


```{r}
hist(dat$sqft_basement, main="Histogram of sqft_basement", xlab="sqft basement")
```
The distribution is right-skewed. 
Log-transforming the variable makes the distribution left-skewed, which 
doesn't help:
```{r}
hist(log(dat$sqft_basement), main="Histogram of log(sqft_basement)",
         xlab="log(sqft_basement)")
```
```{r}
plot(lm(price~sqft_basement, data=dat), which=c(1,2))
```
The residual vs fitted plot doesn't show a linear trend.
This is most likely due to the heavy influence of houses without a basement.
The normal Q-Q plot doesn't show any obvious departures from normality; the 
majority of the points are all fit the line.
### Year built
```{r}
plot(dat$price~dat$yr_built, xlab="year built", ylab="log(price)")
```
It's hard to see the trends very well in this plot, so let's add another column 
in which the yr_built-variable is separated into ranges of 10 years.
```{r}
dat$yr_built_10_range <- cut(dat$yr_built, breaks=seq(1900,2020,10), 
                             labels=c("1900-1910", "1911-1920", "1921-1930", 
                                      "1931-1940", "1941-1950", "1951-1960", 
                                      "1961-1970", "1971-1980", "1981-1990", 
                                      "1991-2000", "2001-2010", "2011-2020"))
# check if it worked: 
head(dat[, c("yr_built", "yr_built_10_range")])
```

```{r}
boxplot(log(dat$price)~dat$yr_built_10_range, 
        xlab="yr_built in ranges of 10 years", ylab="log(price)")
```
Maybe ranges of 20 years make things more visible: 
```{r}
dat$yr_built_20_range <- cut(dat$yr_built, breaks=seq(1900,2020,20), 
                             labels=c("1900-1920", "1921-1940", "1941-1960", 
                                      "1961-1980", "1981-2000", "2001-2020"))
# check if it worked: 
head(dat[, c("yr_built", "yr_built_20_range")])
```
```{r}
boxplot(log(dat$price)~dat$yr_built_20_range, 
        xlab="yr_built in ranges of 20 years", ylab="log(price)")
```
```{r}
cor(dat$price,dat$yr_built)
```
There is no real trend to be seen in the plots. Along with the very low 
correlation coefficient, it seems as the yr_built-feature isn't a good 
indicator for the house price.

Data distribution:
```{r}
summary(dat$yr_built_10_range)
```
```{r}
hist(dat$yr_built, main="Histogram of yr_built", xlab="yr_built")
```
Yr_built doesn't follow a normal distribution. Let's delete the added columns
since they didn't help.
```{r}
dat$yr_built_10_range <- NULL
dat$yr_built_20_range <- NULL
```
```{r}
plot(lm(price~yr_built, data=dat), which=c(1,2))
```

The residual vs fitted plot shows a fairly linear trend.
The normal Q-Q plot doesn't show any obvious departures from normality; the 
majority of the points are all fit the line.
### Year renovated
```{r}
plot(dat$price~dat$yr_renovated, xlab="renovated year", ylab="log(price)")
```

Houses that weren't renovated have a value of dat$yr_renovated==0. This doesn't 
look good in the graph, so let's take a look at samples that have a value != 0.
```{r}
plot(dat[dat$yr_renovated!=0, "price"]~
       dat[dat$yr_renovated!=0, "yr_renovated"],
     xlab="renovation year", ylab="log(price)")
```
```{r}
cor(dat$price,dat$yr_renovated)
```
The yr_renovated-feature isn't a really good predictor. Is it better without 
the samples that weren't renovated?
```{r}
cor(dat[dat$yr_renovated!=0, "price"], dat[dat$yr_renovated!=0, "yr_renovated"])
```
There is no significant change.
Data distribution:
```{r}
hist(dat$yr_renovated, main="Histogram of yr_renovated", xlab="yr_renovated")
```

The data doesn't follow a normal distribution.
```{r}
plot(lm(price~yr_renovated, data=dat), which=c(1,2))
```

It's better to take a look at the data without the houses that weren't 
renovated:
```{r}
plot(lm(dat[dat$yr_renovated!=0, "price"]
        ~dat[dat$yr_renovated!=0, "yr_renovated"], data=dat), which=c(1,2))
```

The residual vs fitted plot shows a fairly linear trend.
The normal Q-Q plot doesn't show any obvious departures from normality; the 
majority of the points are all fit the line.

### Zipcode
```{r}
aggregate(dat$price, list(dat$zipcode), FUN=mean)
```
```{r}
boxplot(dat$price~dat$zipcode, xlab="zipcode", ylab="log(price)")
```

It's difficult to learn something from the zipcode-feature because there are 
many different zipcodes and there is no information on how the zipcodes 
were distributed among the regions (i.e. if similar zipcodes also mean a 
geographical proximity).
However, if assumed that similar zipcodes mean geographical proximity,
it's possible to group the houses by zipcodes and then check if there is a 
more visible trend in the graph:
```{r}
dat$zipcode_20_range <- cut(dat$zipcode, breaks=seq(98000,98200,20), 
                             labels=c("98001-98020", "98021-98040", 
                                      "98041-98060", "98061-98080",
                                      "98081-98100", "98101-98120",
                                      "98121-98140", "98141-98160",
                                      "98161-98180", "98181-98200"))
# check if it worked: 
head(dat[, c("zipcode", "zipcode_20_range")])
```
```{r}
boxplot(dat$price~dat$zipcode_20_range, 
        xlab="zipcodes, grouped in ranges of 20", ylab="log(price)")
```

No real trend can be seen when grouping the zipcodes. 
Data distribution:
```{r}
hist(dat$zipcode, main="Histogram of zipcode", xlab="zipcode")
```

The data doesn't follow a normal distribution.

### Latitude coordinate
```{r}
plot(dat$price~dat$lat, xlab="latitude coordinate", ylab="log(price)")
```

Let's group the coordinates in order to get a better look at possible trends:

```{r}
dat$lat_005_range <- cut(dat$lat, breaks=seq(47.15, 47.80, 0.05), 
                         labels=c("47.11-47.20", "47.21-47.25", "47.26-47.30",
                                  "47.31-47.35", "47.36-47.40", "47.41-47.45",
                                  "47.46-47.50", "47.51-47.55", "47.56-47.60",
                                  "47.61-47.65", "47.66-47.70", "47.71-47.75",
                                  "47.76-47.80"))
head(dat[, c("lat", "lat_005_range")])
```
```{r}
plot(dat$price~dat$lat_005_range, 
     xlab="latitude coordinate in ranges of 0.05", ylab="log(price)")
```

In this plot, it can be seen that the price is maximum for houses with a 
latitude coordinate in the range of 47.61-47.65. Lower and higher latitudes
result in a lower price generally.
```{r}
cor(dat$price, dat$lat)
```
There is a weak-medium positive correlation between the latitude coordinate and
the price of the house.
Data distribution:
```{r}
summary(dat$lat)
```
```{r}
hist(dat$lat, main="Histogram of lat", xlab="lat")
```
The distribution is left-skewed.
```{r}
plot(lm(price~lat, data=dat), which=c(1,2))
```

The residual vs fitted plot shows a fairly linear trend.
The normal Q-Q plot doesn't show any obvious departures from normality; the 
majority of the points are all fit the line.
### Longitude coordinate
```{r}
plot(dat$price~dat$long, xlab="longitude coordinate", ylab="log(price)")
```

Let's group the coordinates once again:
```{r}
# different notation used in order to make the ranges clear
dat$long_01_range <- cut(dat$long, breaks=seq(-122.6, -121.2, 0.1), 
                         labels=c("-122.6<x<=-122.5", "-122.5<x<=-122.4",
                                  "-122.4<x<=-122.3", "-122.3<x<=-122.2",
                                  "-122.2<x<=-122.1", "-122.1<x<=-122.0",
                                  "-122.0<x<=-121.9", "-121.9<x<=-121.8",
                                  "-121.8<x<=-121.7", "-121.7<x<=-121.6",
                                  "-121.6<x<=-121.5", "-121.5<x<=-121.4",
                                  "-121.4<x<=-121.3", "-121.3<x<=-121.2"))
head(dat[, c("long", "long_01_range")])
```
```{r}
boxplot(dat$price~dat$long_01_range, 
        xlab="longitude coordinate in ranges of 0.1", ylab="log(price)")
```
```{r}
cor(dat$price, dat$long)
```
There is almost no correlation between the longitude coordinate and the price.
Data distribution:
```{r}
summary(dat$long)
hist(dat$long, main="Histogram of long", xlab="long")
```
The distribution is right-skewed.
```{r}
plot(lm(price~long, data=dat), which=c(1,2))
```

The residual vs fitted plot shows a fairly linear trend.
The normal Q-Q plot doesn't show any obvious departures from normality; the 
majority of the points are all fit the line.
### Square footage of interior housing of 15 closest neighbors
```{r}
dat$sqft_living15_500_range <- cut(dat$sqft_living15, breaks=seq(0, 6500, 500),
                                   labels=c("1-500", "501-1000", "1001-1500",
                                            "1501-2000", "2001-2500",
                                            "2501-3000", "3001-3500", 
                                            "3501-4000", "4001-4500",
                                            "4501-5000", "5001-5500",
                                            "5501-6000", "6001-6500"))
head(dat[, c("sqft_living15", "sqft_living15_500_range")])
```
```{r}
boxplot(dat$price~dat$sqft_living15_500_range, 
        xlab="square foot of interior housing of 15 closest neighbors in 
        range of 500", ylab="log(price)")
```

```{r}
cor(dat$price, dat$sqft_living15)
```
The positive correlation coefficient supports what can be already seen in the 
graph: a higher number of dat$sqft_living15 goes hand in hand with a higher 
price in general. However, there's one box that goes against that trend in the 
plot above, i.e. the one in the 1-500 range. But that is due to the fact that 
there are only 2 samples in this range and this sould therefore not be regarded
as representative.
Data distribution:
```{r}
summary(dat$sqft_living15)
hist(dat$sqft_living15)
```
The distribution is right-skewed. Log-transforming the variable makes
the histogram left-skewed and therefore is not helpful.
```{r}
plot(lm(price~sqft_living15, data=dat), which=c(1,2))
```

The residual vs fitted plot shows a fairly linear trend.
The normal Q-Q plot doesn't show any obvious departures from normality; the 
majority of the points are all fit the line.
### Square footage of land lots of 15 closest neighbors
```{r}
plot(dat$price~dat$sqft_lot15, 
     xlab="sqft of land lots of 15 closest neighbors", ylab="log(price)")
```

The graph is heavily influenced by the two outliers with a very value of 
sqft_lot15. Let's take a look at the distribution without these extreme 
outliers:
```{r}
tail(sort(dat$sqft_lot15))
```

Let's put the sqft_lot15-feature in ranges. Since most samples seem to 
be below 20000 sqft_lot15, I put all samples with values over 20000 in 
one category and the rest in smaller categories.
```{r}
dat$sqft_lot15_2000_range <- cut(dat$sqft_lot15, 
                                  breaks=c(seq(0, 20000, 2000), +Inf),
                                  labels=c("1-2000", "2001-4000",
                                           "4001-6000", "6001-8000",
                                           "8001-10000", "10001-12000",
                                           "12001-14000", "14001-16000",
                                           "16001-18000", "18001-20000",
                                           ">20000"))

head(dat[, c("sqft_lot15", "sqft_lot15_2000_range")])
```

```{r}
plot(dat$"price"~dat$sqft_lot15_2000_range,
     xlab="sqft of land lots of 15 closest neighbors in 2000 range",
     ylab="log(price)")
```
```{r}
cor(dat$price,dat$sqft_lot15)
```
There is almost no correlation between the sqft_lot15-feature and the price
of the houses. The correlation increases with a log-transformed 
sqft_lot15-variable, so let's do it:
```{r}
dat$sqft_lot15 <- log(dat$sqft_lot15)
```

```{r}
summary(dat$sqft_lot15)
hist(dat$sqft_lot15, main="Histogram of log(sqft_lot15)", 
     xlab="log(sqft_lot15)")
```

This distribution is right-skewed.
```{r}
plot(lm(price~sqft_lot15, data=dat), which=c(1,2))
```

The residual vs fitted plot shows a fairly linear trend.
The normal Q-Q plot doesn't show any obvious departures from normality; the 
majority of the points are all fit the line.

Let's clean the dataframe and remove the created columns that are not needed
for the models:
```{r}
library(dplyr)
dat <- select(dat, -c(sqft_above_1000_range, zipcode_20_range, lat_005_range,
                      long_01_range, sqft_living15_500_range, 
                      sqft_lot15_2000_range))
head(dat)
```
Now, it's time to select the most useful features. Let's take a look at the
correlations with the dependent variable: 
```{r}
vct_corr <- numeric(0)
for (i in names(dat)){
    cor.result <- cor(dat$price, as.numeric(dat[, i]))
    vct_corr <- c(vct_corr, cor.result)
}
names(vct_corr) <- names(dat)
vct_corr
```
Let's remove all features with a low correlation:
```{r}
dat_red <- select(dat, c(price, lat, bedrooms, sqft_basement, view, bathrooms,
                         sqft_living15, sqft_above, grade, sqft_living))
head(dat_red)
```
```{r}
library(GGally)
ggcorr(data=dat_red, label = TRUE, label_size = 3, label_round = 3)
```

The selected features with the highest correlation with price (sqft_living, 
grade, sqft_above and sqft_living15) all have a high correlation with
each other, which has to be kept in mind when working on the model later.
```{r}
ggpairs(dat_red)
```

Now, let's create another dataset without outliers:
```{r}
orig_length <- length(dat$price)
dat_red_out <- dat_red
```
Let's remove the samples for which the lat-value is below the lower
or beyond the upper whisker:
```{r}
b_lat <- boxplot(dat_red_out$lat)
l1 <- length(dat_red_out$price)
dat_red_out <- dat_red_out[dat_red_out$lat >= b_lat$stats[1] &
                       dat_red_out$lat <= b_lat$stats[5], ]
l2 <- length(dat_red_out$price)
sprintf("previous no. of samples: %s, new no. of samples: %s, new dataset contains %.2f%% of the samples of the previous dataset", l1, l2, (100*l2)/l1)
```

Let's repeat that for the other features as well:
```{r}
b_bedrooms <- boxplot(dat_red_out$bedrooms)
l1 <- length(dat_red_out$price)
dat_red_out <- dat_red_out[dat_red_out$bedrooms >= b_bedrooms$stats[1] &
                       dat_red_out$bedrooms <= b_bedrooms$stats[5], ]
l2 <- length(dat_red_out$price)
sprintf("previous no. of samples: %s, new no. of samples: %s, new dataset contains %.2f%% of the samples of the previous dataset", l1, l2, (100*l2)/l1)
```

```{r}
b_sqft_basement <- boxplot(dat_red_out$sqft_basement)
l1 <- length(dat_red_out$price)
dat_red_out <- dat_red_out[dat_red_out$sqft_basement >= b_sqft_basement$stats[1] &
                       dat_red_out$sqft_basement <= b_sqft_basement$stats[5], ]
l2 <- length(dat_red_out$price)
sprintf("previous no. of samples: %s, new no. of samples: %s, new dataset contains %.2f%% of the samples of the previous dataset", l1, l2, (100*l2)/l1)
```

Since the view-feature isn't continuous and only has 5 levels, it doesn't make 
sense to remove outliers based on a boxplot for this feature.
```{r}
b_bathrooms <- boxplot(dat_red_out$bathrooms)
l1 <- length(dat_red_out$price)
dat_red_out <- dat_red_out[dat_red_out$bathrooms >= b_bathrooms$stats[1] &
                       dat_red_out$bathrooms <= b_bathrooms$stats[5], ]
l2 <- length(dat_red_out$price)
sprintf("previous no. of samples: %s, new no. of samples: %s, new dataset contains %.2f%% of the samples of the previous dataset", l1, l2, (100*l2)/l1)
```
```{r}
b_sqft_living15 <- boxplot(dat_red_out$sqft_living15)
l1 <- length(dat_red_out$price)
dat_red_out <- dat_red_out[dat_red_out$sqft_living15 >= b_sqft_living15$stats[1] &
                       dat_red_out$sqft_living15 <= b_sqft_living15$stats[5], ]
l2 <- length(dat_red_out$price)
sprintf("previous no. of samples: %s, new no. of samples: %s, new dataset contains %.2f%% of the samples of the previous dataset", l1, l2, (100*l2)/l1)
```

```{r}
b_sqft_above <- boxplot(dat_red_out$sqft_above)
l1 <- length(dat_red_out$price)
dat_red_out <- dat_red_out[dat_red_out$sqft_above >= b_sqft_above$stats[1] &
                       dat_red_out$sqft_above <= b_sqft_above$stats[5], ]
l2 <- length(dat_red_out$price)
sprintf("previous no. of samples: %s, new no. of samples: %s, new dataset contains %.2f%% of the samples of the previous dataset", l1, l2, (100*l2)/l1)
```

```{r}
b_grade <- boxplot(dat_red_out$grade)
l1 <- length(dat_red_out$price)
dat_red_out <- dat_red_out[dat_red_out$grade >= b_grade$stats[1] &
                       dat_red_out$grade <= b_grade$stats[5], ]
l2 <- length(dat_red_out$price)
sprintf("previous no. of samples: %s, new no. of samples: %s, new dataset contains %.2f%% of the samples of the previous dataset", l1, l2, (100*l2)/l1)
```

```{r}
b_sqft_living <- boxplot(dat_red_out$sqft_living)
l1 <- length(dat_red_out$price)
dat_red_out <- dat_red_out[dat_red_out$sqft_living >= b_sqft_living$stats[1] &
                       dat_red_out$sqft_living <= b_sqft_living$stats[5], ]
l2 <- length(dat_red_out$price)
sprintf("previous no. of samples: %s, new no. of samples: %s, new dataset contains %.2f%% of the samples of the previous dataset", l1, l2, (100*l2)/l1)
```

```{r}
sprintf("Overall, the dataset contains now - after removing outliers - %.2f%% of the samples of the original dataset", (100*l2)/orig_length)
```
To get an overview over the relationships between the selected features and the 
dependent variable:
```{r}
ggcorr(data=dat_red_out, label = TRUE, label_size = 3, label_round = 3)
```
```{r}
ggpairs(dat_red_out)
```

It can be seen that there are some really strong correlations between
some of the variables, which has to be kept in mind when building the models.

# The Models
## Model 1
Idea: 
predict price with all the other variables taken into account
(i.e. price~lat+bedroom+...+sqft_livng) for the two
datasets dat_red and dat_red_out. Compare the results and improve on the better
model. For the next models, we should take the correlation inbetween the 
variables into account (see the ggcorr-plot above).
```{r}
model_1 = lm(price ~ ., data=dat_red)
summary(model_1)
```
We can see that the bathrooms-feature doesn't give us a good result, so 
we're going to remove it. 
```{r}
dat_red$bathrooms<-NULL
```
```{r}
model_1 = lm(price ~ ., data=dat_red)
summary(model_1)
```
This model gave us a 0.73 R-squared value, let's try to improve it.
## Model 2
Let's now try using dat_red_out, which is the dataset after removing the 
outliers.
```{r}
model_2 = lm(price ~ ., data=dat_red_out)
summary(model_2)
```
```{r}
dat_red_out$bathrooms <- NULL
```
```{r}
model_ = lm(price ~ ., data=dat_red_out)
summary(model_2)
```
The dataset with the outliers (dat_red) gave us a significantly better result 
(higher R-squared value), so we're gonna stick with it for the next iterations.
## Model 3
The effect of sqft_above (sqft of the house without the basement) may not be 
constant throughout all values (in fact we could see when plotting it with 
price that their relation wasn't quite linear), therefore we will introduce a 
higher-order term by creating a new variable.
```{r}
dat_red$sqft_above2 <- dat_red$sqft_above^2
```
```{r}
model_3 = lm(price ~ ., data=dat_red)
summary(model_3)
```
This model has a slightly better R-squared result than model 1. 
## Model 4
It makes sense for houses with basement to have a higher price than houses 
without it. Let's add that new variable.
```{r}
dat_red$basement <- ifelse(dat_red$sqft_basement>0, 1,0)
```
```{r}
model_4 = lm(price ~ ., data=dat_red)
summary(model_4)
```
The R-squared value has not improved.
## Model 5
It could be that grade has a combined impact with other variables, for example 
if the house has two or more floors and the grade is good, the price would be 
higher. 
```{r}
dat_red$floors2 <- ifelse(dat$floors >= 2, 1, 0)
dat_red$grade10 <- ifelse(dat_red$grade >= 10, 1, 0)
```
We've also added back waterfront with the premise that if the grade of the 
house is good and it has a view to a waterfront, the price will be higher.
```{r}
model_5 = lm(price ~ . +floors2*grade10+dat$waterfront*grade10, data=dat_red)
summary(model_5)
```
The model has slightly improved the value of R-squared.
### Model 6
Let's start again and use the dataset with all the variables, since even if 
they don't have a correlation with price it could be that some relationships 
between them do have a correlation.
```{r}
model_6 = lm(price ~ . , data=dat)
summary(model_6)
```
The R-squared value has improved.

### Model 7
Let's now add the improvements that we used before.
```{r}
model_7 = lm(price ~ . +dat_red$sqft_above2
             +dat_red$floors2*dat_red$grade10+waterfront*dat_red$grade10, 
             data=dat)
summary(model_7)
```
The R-squared value has slightly improved. 
Now, let's add an interaction term for sqft_above and sqft_basement, since
there there is correlation between these variables as shown earlier.
```{r}
model_8 <- lm(price ~ . +dat_red$sqft_above2
              +dat_red$floors2*dat_red$grade10
              +waterfront*dat_red$grade10
              +dat_red$sqft_above*dat_red$sqft_basement, data=dat)
summary(model_8)
```
The R-squared value has improved.
# Conclusion




